An agent-based model of military mechanization

### 2018-07-12 paper2/paper2.tex
progress

Why ABM:
 - inadequacy of SS - VIF, linear model
 - uncertainty of causation
 - endogeneity
 - GDP / capita explains this...but also everything else
 - have to go with simulation
 - bigger picture, world politics as complex system
 - look at Axtell \citep{axtell2000agents}

@@

There is reason to believe that the orthodox multivariate statistical modeling 
approach employed in \citet{sechser2010army} is insufficient. Several factors point towards 
agent-based modeling being a more appropriate choice.

One, from a stat

>>>>

Why ABM:
 - inadequacy of SS - VIF, linear model
 - uncertainty of causation
 - endogeneity
 - GDP / capita explains this...but also everything else
 - have to go with simulation
 - bigger picture, world politics as complex system
 -

@@

There is reason to believe that the orthodox multivariate statistical modeling 
approach employed in \citet{sechser2010army} is insufficient and leads to
incorrect conclusions.

One, from a statistical perspective, the ability of the model in
\citet{sechser2010army} to produce reliable insight is questionable.
Observational data. Selection into war and deterrence.

Two, linear model poorly suited to represent the complex interactions. List
some. GDP/capita to democracy to war to mechanization. Internal politics to
external politics to mechanization. Emulation and network effects.

Agent-based modeling more appropriate.

look at Axtell \citep{axtell2000agents}

Other studies have already done it.
